Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium revision (\YellowPaperVersionNumber{})}}

### 2018-02-01 Paper.tex
\hypertarget{block_reward_R__b}{}
\hypertarget{Gamma}{}

\hypertarget{block-reward-R-b}{block-reward-R-b}We define the block reward as 3 Ether:
\begin{equation}
\text{Let} \quad R_b = 3 \times 10^{18}
\end{equation}

@@

\hypertarget{Gamma}{Gamma}We may now define the function, $\Gamma$, that maps a block $B$ to its initiation state:
\begin{equation}
\Gamma(B) \equiv \begin{cases}
\boldsymbol{\sigma}_0 & \text{if} \quad P(B_H) = \varnothing \\
\boldsymbol{\sigma}_i: \mathtt{\small TRIE}(L_S(\boldsymbol{\sigma}_i)) = {P(B_H)_H}_r & \text{otherwise}
\end{cases}
\end{equation}

>>>>

\hypertarget{block_reward_R__b}{}We define the block reward as 3 Ether:
\begin{equation}
\text{Let} \quad R_b = 3 \times 10^{18}
\end{equation}

@@

\hypertarget{Gamma}{}We may now define the function, $\Gamma$, that maps a block $B$ to its initiation state:
\begin{equation}
\Gamma(B) \equiv \begin{cases}
\boldsymbol{\sigma}_0 & \text{if} \quad P(B_H) = \varnothing \\
\boldsymbol{\sigma}_i: \mathtt{\small TRIE}(L_S(\boldsymbol{\sigma}_i)) = {P(B_H)_H}_r & \text{otherwise}
\end{cases}
\end{equation}
